As discussed in Chapter \ref{Intro}, the Reference Architecture is intended to improve CubeSat system designs by providing a starting point and a framework that guides teams through the entire systems engineering process. The tool will have AFIT students in mind with some course-specific features, but will also serve as a general CubeSat Reference Architecture outside of AFIT. To understand the organization and unique features of this Reference Architecture, it's helpful to understand the primary goals, inputs, and outputs of the course sequence. 

At AFIT, the first course starts with teams given a \abbreviationFull[Mission Capabilities Document]{MCD} for a fictional or real mission, which outlines the "Mission Need Statement," "Operational Context," and a set of required capabilities and design constraints. From this set of inputs, students develop stakeholder concerns and needs, perform trade studies, write a \abbreviationFull[Concept of Operations]{CONOPS}, and finally develop a set of mission requirements. These artifacts are carried into the next course, where system level requirements are defined and a physical structure is designed. Finally, in the third course, students take those system-level requirements and further define subsystem-level requirements and develop test plans to verify those requirements. These courses are intended to flow together, and this Reference Architecture will help by providing the model framework to carry between and support all three courses. Throughout the course sequence, there are also milestone reviews and stakeholder documentation requirements to fulfill. 

Students in this course sequence use the textbook Space Mission Engineering: The New Space Mission Analysis and Design by Wertz, et al \citep{Wertz2011SpaceSMAD}. Wertz focuses mainly on the requirements definition and validation portion of the Systems Engineering process, so other more general Systems Engineering texts were consulted to supplement Wertz, such as those by Friedenthal \citep{FriedenthalPracticalGuide}, Buede \citep{Buede2016}, and Maier and Rechtin \citep{MaierRechtin}. 


The Space Vehicle design sequence, as taught by AFIT, has one primary input, the MCD. From there, the following outputs are generated as part of the process. Each report, trade study, review and artifact will have a place in the Reference Architecture.

\begin{table}[H]
\centering
\begin{tabular}{|l|l|}
\hline
\textbf{Reports}                    & \textbf{Trade Studies}     \\
\hline
Mission Capabilities Document       & Constellation Trade Study  \\
Stakeholder Analysis Report         & Delta V Analysis           \\
Concept of Operations               & Launch Vehicle Trade Study \\
Space Vehicle Requirements Document & RF Link Budget Analysis    \\
Operational Requirements Document   & Mass Budget                \\
Subsystem Test Plans                & Power Budget               \\
Subsystem Test Reports              & Cost Budget                \\
Flight Readiness Review Report      & Schedule                   \\
\hline
\textbf{Reviews}                    & \textbf{Other Artifacts} \\
Mission Concept Review              & Cameo System Model \\
Preliminary Design Review           & Digital Drawing \\
Critical Design Review              & STK Simulation \\
Test Readiness Review               & OV-1 Diagram\\
Flight Readiness Review             & \\
\hline
\end{tabular}
\caption{Design Outputs}
\label{table:Design Outputs}
\end{table}

This list is not exhaustive, as differing missions or stakeholders may need different outputs, so the Reference Architecture is designed to be flexible enough for unforeseen variations. In addition to these formal documents and reviews, the model itself is useful for describing the physical decomposition and interfaces of the system. The model itself holds all the text, figures, tables, and trade studies that are used in the documents as well. For example, the CONOPS document goes through mission and fault phases, describing subsystem conditions, detailing activity diagrams for those phases, and writing narratives to describe activities. These are all contained in model elements, and the document just calls these elements in the appropriate format for display. 

Table \ref{table:CubeSat Development Process} briefly outlines what the typical CubeSat development process looks like \citep{NASA101}, and Table \ref{table:AFIT CubeSat Development Process} shows the process done in the short time frame of the design sequence at AFIT. This CubeSat design process at AFIT is coinciding with normal academic instruction and labs unrelated to the CubeSat project, so the timeframes do not cover the entire nine months. 

\begin{table}[H]
\centering
\begin{tabular}{|l|l|c|} 
 \hline
 Step & Project Phase & Typical Timeframe \\ [0.5ex] 
 \hline\hline
 1 & Concept Development & 1-6 months\\
 2 & Securing Funding & 1-12 months\\
 3 & Merit and Feasibility Review & 1-2 months\\
 4 & CubeSat Design & 1-6 months\\
 5 & Development and Submittal of Proposal & 3-4 months\\
 6 & Selection and Manifesting & 1-36 months\\
 7 & Mission Coordination & 9-18 months\\
 8 & Licensing & 4-5 months\\ 
 9 & Flight Specific Documentation Development & 10-12 months\\
 10 & Ground Station Design, Development and Test & 2-12 months\\ 
 11 & CubeSat Hardware Fabrication and Testing & 2-12 months\\
 12 & Mission Readiness Review & Half day\\
 13 & CubeSat to Dispenser Integration and Testing & 1 day\\
 14 & Dispenser and Launch Vehicle Integration & 1 day\\
 15 & Launch & 1 day\\
 16 & Mission Operations & Variable, up to 2 years\\
 \hline
\end{tabular}
\caption{Typical CubeSat Development Process}
\label{table:CubeSat Development Process}
\end{table}


\begin{table}[h!]
\centering
\begin{tabular}{|l|l|c|} 
 \hline
 Step & Project Phase & Typical Timeframe \\ [0.5ex] 
 \hline\hline
 1 & Stakeholder Analysis & 2 weeks\\
 2 & Risk Identification & 2 weeks\\
 3 & Trade Studies & 2 weeks\\
 4 & Mission Phases & 1 week\\
 5 & Fault Management & 1 week\\
 6 & Concept of Operations & 1 week\\
 7 & Mission Concept Review & Half day\\
 8 & Space Vehicle Requirements Document & 2 weeks\\
 9 & Mass and Power Budgets & 1 week\\
 10 & Preliminary Design Review & Half day\\
 11 & Physical Design & 2 months\\
 12 & Critical Design Review & Half day\\
 13 & Subsystem Test Plans & 3 weeks\\
 14 & CubeSat Hardware Fabrication and Testing & 3 months\\
 15 & Flight Readiness Review & Half day\\
 \hline
\end{tabular}
\caption{AFIT CubeSat Development Process}
\label{table:AFIT CubeSat Development Process}
\end{table}